---
title: "Alcohol vs Seat choice"
author: "Marina Ornelas"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy notch displays the three categories of seating arrangements which was the front, back and middle. We can observe that the people who were seated in the back had a median that differed while the people in the front and back had a more confident median plot. We can assume that the people in the back have a higher average of consuming alcoholic drinks compared to those who were seated in the middle and front rows. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical data shows that the average number of drinks for the people who are seated in the back is about 9 drinks. This is 3 times the average number of drinks for those who are seated in the middle. This is also 9 times the average number of drinks for those who are seated in the front. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential test shows a small number of P-value with 0.000116, which means that this is the probability of having no difference between alcohol consumed between the 3 row options: front, middle and back, that are available for people to be seated in. 

```{r}
plot(TukeyHSD(model1))
```

This plot shows that there is a difference in the alcohol consumed between the three sections that a person can be seated in. The intervals from the front and back cross which tells us that there is not a significant difference between these two sections. On the other hand, the intervals of the back and front never cross as well as the back and middle, telling us that there is a significant difference between the amount of drinks per section. 

## Conclusions
After looking over the numerical data and inferential tests we can conclude that the people who are seated in the back section are consuming more alcohol than those who are seated in the front of middle sections. The numerical data shows that there is an average of 9 drinks on average being consumed in the back sections while we have 3 drinks being averaged for the middle section and 1 drink averaged for the front section. We also got a p-value of 0.000116 which indicates that there is almost no chance of having no differences between the amount of drinks consumed by people in each section. 

